Preliminary Draft

### 2021-07-20 article/draft.tex
updates

Hence, in the present article, we focus on mainstream platforms' policies and interventions regarding content with low credibility or false information, commonly referred to as {\it Fake News} (see Lazer et al. (2018)~\cite{lazer}). The {\it Fake News} phenomenon is still ill-defined by the academic community, as it encompasses several combined features such as spreading inaccurate, false or misleading information, with or without the intention of influencing or manipulating a target pool of audience.  The growth of social networking platforms over the last decade in terms of number of users worldwide and volume of content, has modified the information ecosystem in terms of production of information and its mediation. Many users can now produce and share content which includes news related information, without having to abide by strict editorial processes that ensure accuracy of information and reliability of sources. In particular, false or inaccurate content produced and shared on social networking platforms concerning the political life or public health may have a potentially harmful impact on the society, in the rare event that it goes viral. This gave rise to a set of heterogenous fact-checking policies across mainstream platforms. For example, Facebook has a substantial partnership program with Fact-checking partners certified by the non-partisan International Fact-Checking Network. Facebook uses a number of signals and machine learning models to predict misinformation and surface it to fact-checkers.\footnote{See the \href{https://www.facebook.com/journalismproject/programs/third-party-fact-checking/how-it-works}{section} Frequently asked questions: `How does Facebook use technology to detect potential misinformation?''} Twitter seems to have a different approach where they focus on providing context rather than fact-checking\footnote{To the best of our knowledge, Twitter does not have a page which summarizes its fact-checking strategy. The Twitter Safety Team tweeted on June 3, 2020 the following:  ``We heard: 1. Twitter shouldn’t determine the truthfulness of Tweets 2. Twitter should provide context to help people make up their own minds in cases where the substance of a Tweet is disputed. Hence, our focus is on providing context, not fact-checking.'' Tweet ID \href{https://twitter.com/TwitterSafety/status/1267986503721988096}{1267986503721988096}.} and the platform is testing a new system based on the wisdom of the crowds to tackle misinformation (see \href{https://blog.twitter.com/en\_us/topics/product/2021/introducing-birdwatch-a-community-based-approach-to-misinformation}{Twitter Birdwatch}). As for Youtube, this platform utilizes the \href{https://schema.org/ClaimReview}{schema.org ClaimReview} markup, where fact-checking articles created by eligible publishers can appear on information panels (see table \ref{summary} in Appendix \ref{links}).

@@

During the COVID19 global health pandemic platforms have upgraded their guidelines to include a set of rules to tackle the propagation of potentially harmful content (see table \ref{summary} in Appendix \ref{links}). Those policies are enforced via existing actions used by the platforms to tackle other rules' violations, such as: labelling content to provide more context or indicate falsehood, publishing a list of terms or topics that will be flagged\footnote{{\color{pink} put here the list of Facebook and Twitter terms about covid.}}, suspending accounts, implementing strike systems, reducing the visibility of content, etc. As each platform is a private company, those {\it new} policies are not coordinated and are implemented in different ways across platforms. Such targeted policies show the willingness of mainstream platforms to enhance the quality of the online conversation, but also sheds light on the lack of specific policies to tackle misinformation in general. In particular, policies regarding misinformation are not part of the set of platform rules or community guidelines\footnote{As of July 2021.}. The 2019 report of the Facebook Data Transparency Advisory Group (DTAG) states that ``{\it DTAG was not tasked with evaluating any of the following: (...) Facebook’s policies with respect to “fake news” or misinformation, as neither of these categories were counted as violations within the first two versions of the Community Standards Enforcement Report.}''. Facebook's strategy to tackle ``False News'' is three fold : Remove, Reduce, Inform. It is explained via a blog post on the facebook Newsroom. Similarly, Twitter communicates about actions related to misinformation via their \href{https://blog.twitter.com/en\_us/authors.TwitterSafety}{Twitter Safety} Blog/account. In a post on Youtube Official Blog, the platform explained its ``Four Rs of Responsibility" and how it raises authoritative content, reduces borderline content and harmful misinformation (see table \ref{summary} in Appendix \ref{links}).

@@

Nevertheless, misinformation specific interventions by mainstream platforms are hard to monitor, study or verify by third parties (e.g. academic community, data journalists, NGOs), as in many cases misleading or false content does not qualify as a violation of a given platform's rules and it does not explicitly appear as a separate category in available transparency reports. This makes the study of online misinformation, the assessment of the impact of platforms' actions to tackle misinformation and their relevancy a burdensome task for the academic community. Hence, in the present article we explain how to verify with data mining mainstream platforms' current actions regarding content with low credibility or false information. We do so by providing a series of examples for different interventions and platforms. We only focus on three platforms: Facebook, Twitter and Youtube. Both Facebook and Youtube are in the top three most popular social media platforms in terms of number of users.\footnote{See for example the ranking of the most popular social networks as of April 2021 on Statista: \href{https://www.statista.com/statistics/272014/global-social-networks-ranked-by-number-of-users/}{https://www.statista.com/statistics/272014/global-social-networks-ranked-by-number-of-users/}.} We further choose Twitter because it is a social networking platform with the most news-focused users, according to the Pew Research center (2019)~\cite{pew1}. More specifically, we survey a number of common policies used in order to tackle misinformation, across the three above cited mainstream platforms, Facebook, Twitter and Youtube: temporary or permanent suspension of users, reducing the visibility of some content, introducing flags and notices. We do not provide  an exhaustive list of methods on how to investigate the platforms’ policies.\footnote{For a detailed list of interventions check the following \href{https://airtable.com/shrO0ooI9WSEfIUhb/tblAWQwFOiihKdQjm/viwZLAOzLK1NQ0c2n?blocks=hide}{airtable} compiled by Slatz and Leibowicz (2021)~\cite{niemanlab}. } We rather provide a methodology to investigate key policies, that can be useful to researchers or journalists interested in implementing external monitoring. We summarize in table \ref{tab1} the tools used to collect the data from Facebook, Twitter and Youtube, that we use in multiple examples throughout the present article. We compile in Appendix \ref{links} in table \ref{summary}, a list of links that redirect to the policies, regulations and transparency centers of Facebook, Twitter and Youtube that we discuss throughout the article. Finally, we discuss how an increased effort of transparency regarding specific content can help the community of researchers study and assess the impact of platforms' policies regarding misinformation.  %the announced policy for a specific user was implemented or not.

@@

Mainstream social media platforms may suspend the account of a specific user when they deem that the platforms' rules have been violated. Account suspension can be temporary or permanent.\footnote{A list of notable Twitter temporary and permanent suspensions can be found on wikipedia: \href{https://en.wikipedia.org/wiki/Twitter_suspensions}{https://en.wikipedia.org/wiki/Twitter\_suspensions}.}  When the suspension is temporary the user is prohibited for a limited period of time from posting content on their account, but created content prior to suspension remains available to the user and their followers. However, when the suspension is permanent, in most cases, followers or subscribers have no longer access to the content prior to the suspension and the user can no longer use the account to create new content.  In what follows, we focus on the implementation of this policy by several platforms and provide simple examples to illustrate.

@@

Facebook can also apply a temporary suspension, and in this case the data can often be collected and analyzed. For example, \href{https://www.facebook.com/DonaldTrump/}{Donald Trump’s official Facebook page}  has been suspended following the Capitol attack on January 6, 2021.\footnote{See \href{https://www.facebook.com/zuck/posts/10112681480907401}{https://www.facebook.com/zuck/posts/10112681480907401}} Nevertheless the page’s data is still present in the CrowdTangle API. Thus, after manually adding this page to the CrowdTangle dashboard, we collected the $6$ $083$ posts it had published between January $1$, $2020$ and June $15$, $2021$ using the {\it posts} endpoint.\footnote{See the endpoint documentation for more details: \href{https://github.com/CrowdTangle/API/wiki/Posts}{https://github.com/CrowdTangle/API/wiki/Posts}.} We used Minet command line tool \cite{minet} to collect the data.\footnote{The exact command can be found \href{https://github.com/medialab/truth-and-trust-online-2021/blob/master/code/collect_facebook_crowdtangle_trump_data.sh}{here}.} We can verify on figure \ref{fig1_fb} that the {\it Donald J. Trump} page has not published any content since January $6$, 2021, and that this behavior is not consistent with the page’s previous activity: an average of $16$ posts were published each day on Facebook before the suspension.

@@

%paragraph strike system + say following example is a manual decision. 
Twitter has implemented a strike system as part of their Civic Integrity Policy and their COVID19 misleading information policy. Violations of both policies can entail strikes, where two strikes lead to a 12-hour account lock and five or more strikes lead to permanent suspension from the platform. The 12-hour account lock is hard to observe in the data, especially for users who do not have an over the clock tweeting activity. In this section, we provide one example of a temporary suspension\footnote{See the official documentation on the Twitter's Help Center regarding account suspension: \href{https://help.twitter.com/en/managing-your-account/suspended-twitter-accounts}{https://help.twitter.com/en/managing-your-account/suspended-twitter-accounts }.} of a Twitter account, that seems to be the result of a manual decision concerning a Tweet which violated the rules.

The Twitter account $@LifeSite$ of the website lifesitenews.com has been suspended for at least two periods of time: from end of 2019 until fall 2020 for 308 days, then again since January 2021 for having violated Twitter Rules\footnote{See Lifesitenews's article discussing the reason for the suspension: \href{https://www.lifesitenews.com/news/lifesite-is-dumping-twitter-and-so-should-you}{https://www.lifesitenews.com/news/lifesite-is-dumping-twitter-and-so-should-you}. Twitter rules can be found at: \href{https://help.twitter.com/en/rules-and-policies/twitter-rules}{https://help.twitter.com/en/rules-and-policies/twitter-rules}. }. In particular, this website has several failed fact-checks concerning the published articles, according to Iffy.news.\footnote{See \href{https://mediabiasfactcheck.com/life-site-news/}{https://mediabiasfactcheck.com/life-site-news/}}. We collected the activity (tweets, replies, quotes, retweets) on their Twitter account via the Twitter API, using the historical search endpoint.\footnote{See the documentation: \href{https://developer.twitter.com/en/docs/twitter-api/tweets/search/api-reference/get-tweets-search-all}{https://developer.twitter.com/en/docs/twitter-api/tweets/search/api-reference/get-tweets-search-all}.} We then plotted the number of Tweets, Retweets, Quotes and Replies per day, as shown in panel $a$ of figure \ref{fig2}). The two periods of temporary suspension are clearly observed in the data as the user(s) of the account were not allowed to use the functionalities of the Twitter Platform.

@@

In this section, we turn to the channel's temporary or permanent suspension policy of Youtube. Whenever a channel publishes a video that violates the community guidelines for the first time they will  usually receive a warning and the content will be removed. For the second time the channel will start receiving strikes. A first strike results in limiting the access of the Youtube channel  for one week, like uploading videos, streaming and other activities. Then a second strike is similar but the suspension will be for two weeks. A third strike results in the termination of the channel. The strike count of a channel lasts 90 days.  In the special case, where a video is in extreme violation of the guidelines, the publishing channel may get terminated without a warning.\footnote{See the ``Community Guidelines strike basics''. Youtube help, Google Developers,  \href{https://support.google.com/youtube/answer/2802032?hl=en. Accessed 21 6 2021}{https://support.google.com/youtube/answer/2802032?hl=en. Accessed 21 6 2021}.} To illustrate the implementation of this policy we provide two examples for the temporary suspension of the following two Youtube channels: \href{https://www.youtube.com/channel/UCNbIDJNNgaRrXOD7VllIMRQ}{One America news Network} and \href{https://www.youtube.com/user/TonyHeller1}{Tony Heller}.

@@

First, we investigate the temporary suspension case of the Youtube Channel of {\it One America News channel}. This channel received a first strike on November 24, 2020 for the promotion of  a false cure for COVID19.\footnote{See nbcnews,  \href{https://www.nbcnews.com/news/all/youtube-suspends-oann-violating-its-covid-19-policy-n1248845}{YouTube suspends OANN for violating its Covid-19 policy} nbcnews, Ahiza García-Hodges, 24 11 2020.} We collected the activity of the channel OANN (video counts, view counts) using  the Youtube API v3, between November 2020 and January 2021. For the video counts, we used the playlist endpoint to retrieve the videos uploaded with their publishing date and for the view count we used the IDs of the videos we had from the playlists and via the videos endpoint we retrieved the view counts on June 2021.\footnote{See the Google documentation  \href{https://developers.google.com/youtube/v3/docs/videos/list}{https://developers.google.com/youtube/v3/docs/videos/list} and \href{https://developers.google.com/youtube/v3/docs/playlists/list}{https://developers.google.com/youtube/v3/docs/playlists/list}}

@@

We first searched for all the Facebook posts having shared a link rated as ‘False’ by Science Feedback with the {\it search} endpoint in minet\footnote{ link: \href{https://beforeitsnews.com/eu/2021/04/stay-away-from-the-vaxxed-it-is-official-from-pfizers-own-documents-2671454.html}{https://beforeitsnews.com/eu/2021/04/stay-away-from-the-vaxxed-it-is-official-from-pfizers-own-documents-2671454.html} and its fact-check: \href{https://healthfeedback.org/claimreview/insufficient-evidence-to-claim-covid-19-vaccines-cause-menstrual-irregularities-in-vaccinated-women-vaccinated-people-arent-making-unvaccinated-people-ill/}{https://healthfeedback.org/claimreview/insufficient-evidence-to-claim-covid-19-vaccines-cause-menstrual-irregularities-in-vaccinated-women-vaccinated-people-arent-making-unvaccinated-people-ill/}).}. Twenty Facebook posts were collected this way, and the newly developed scraper was used to verify whether they were flagged with an information banner, a fact-check flag, both or none. Three posts were unavailable, and thus could not be categorized by the scraper. As Science Feedback has sent a False fact-check for this link to Facebook, we would expect all these posts to contain a fact-check flag, but we had no expectations for the information banner.

@@

Alongside other social networking platforms, when the content of a tweet violates the Twitter rules, a notice can be added to provide more context according to Twitter's Help Center.\footnote{See Notices on Twitter and what they mean: \href{https://help.twitter.com/en/rules-and-policies/notices-on-twitter}{https://help.twitter.com/en/rules-and-policies/notices-on-twitter}.} At the tweet level, notices take the form of a label or an interstitial. Labels are context specific (e.g. COVID19 or presidential elections) and  redirect users to a URL to get more context, for example ``Get the facts about COVID-19'' (see right panel of figure \ref{fig8}). Interstitials are presented as a greyed box on top of a tweet, which indicate sensitive content, violations of Twitter rules, withheld tweets for violation of local laws or even tweets from suspended accounts, for example ``The following media includes potentially sensitive content'' (see left panel of figure \ref{fig_notice}). At the account level, notices can also indicate whether an account has been temporarily or permanently suspended.

@@

\begin{figure}[h]
\centering
	%\begin{multicols}{1}
		\includegraphics[scale=0.35]{./img/tweets/Capture_2021-06-30_2.png}
   	 %\end{multicols}
	%\begin{multicols}{1} 
		\includegraphics[scale=0.32]{./img/tweets/Capture_2021-06-30.png}
	%\end{multicols}
	\caption{Two tweets sharing the same URL link marked as False by a Fact-Checker, screenshots taken on June 20, 2021. Panel (a): Tweet ID \href{https://twitter.com/davidjcaron/status/1241088065462026242}{1241088065462026242} without a label. Panel (b): Tweet ID \href{https://twitter.com/reactiveIntent/status/1261876171584745472}{1261876171584745472} containing a label.}
	\label{fig8}
\end{figure}

@@

In this section, we take a deeper look at how labels and notices are introduced by Twitter, to indicate content which is inaccurate or false. To that end, we gathered a set of $3094$ URL links of articles which were marked as $False$ by Science Feedback, a fact-checking organization verifying the credibility of science-related viral information. As a second step, we collected (on June 30, 2021) via Minet Command line tool~\cite{minet} all the tweets that have shared a URL link which belongs to the set of $3094$ links marked as $False$. This data collection resulted in $323$ $938$ tweets, excluding retweets. Only $28$ tweets contained the label { ``Get the facts about COVID-19''}, $5$ tweets contained the label { ``Learn about US 2020 election security efforts''} and only $1$ had the following label {``This claim about election fraud is disputed''}. Furthermore, we noticed that the labeling rule might not be applied uniformly on a given set of tweets sharing the exact same URL link, among the set of collected tweets. More specifically, exactly $657$ tweets had shared a URL link redirecting to a video on Bitchute, entitled ``Important information on coronavirus 5G Kung Flu''. Among those $657$ tweets only $3$ contained the label ``Get the facts about COVID-19'' (see figure \ref{fig8}). This points towards the non-automation of the tweet labelling process and that it might be that these $3$ tweets were the only ones reported by a user.

@@

We further examine the placement of interstitials that indicate a possibly sensitive content. We find that only $2.97\%$ out of $323$ $938$ tweets containing a URL marked as False, have an interstitial ``potentially sensitive content''. {\color{pink}In particular, many tweets speak about COVID19 and do not contain a label to provide users with more context from authoritative sources. Figure \ref{fig_notice} provides an example of a tweet sharing a URL marked as False by a Fact-checker and which contains an interstitial ``potentially sensitive content''.} We find 32 other Tweets, among our set of collected tweets, who share the exact same URL link as in the previous example. Among those 32 Tweets, only 5 tweets had the interstitial ``potentially sensitive content''. Again this points towards the non-automation of the placement of interstitials.\footnote{Notice that the appearance of interstitials may depend on the settings of a user's account and country or language specific regulations. In particular, in the settings of Twitter account, one can deactivate the display of interstitials for {\it sensitive content}, by ticking the box {\it Display media that may contain sensitive content} in the section {\it content you see}. Hence the numbers given are an upper bound of the number of interstitials indicating  possibly sensitive content.} 
{\color{pink} can we have both at the same time (see example facebook)  + dire pour l'exemple get the facts about covid. }
\smallskip

Finally, Twitter Safety account announced in a Tweet\footnote{See Tweet ID : \href{https://twitter.com/TwitterSafety/status/1379515615954620418}{1379515615954620418}} on April 6, 2021 that their team ``will begin deploying automated tools to build on (their) efforts to label tweets that may contain misleading information around COVID-19 vaccinations". 
%we don't know what it means the article xxx which was retracted by the journal and fack-check still appears in xx tweets with no label

>>>>

Hence, in the present article, we focus on mainstream platforms' policies and interventions regarding content with low credibility or false information, commonly referred to as {\it Fake News} (see Lazer et al. (2018)~\cite{lazer}). The {\it Fake News} phenomenon is still ill-defined by the academic community, as it encompasses several combined features such as spreading inaccurate, false or misleading information, with or without the intention of influencing or manipulating a target pool of audience.  The growth of social networking platforms over the last decade in terms of number of users worldwide and volume of content, has modified the information ecosystem in terms of production of information and its mediation. Many users can now produce and share content which includes news related information, without having to abide by strict editorial processes that ensure accuracy of information and reliability of sources. In particular, false or inaccurate content produced and shared on social networking platforms concerning the political life or public health may have a potentially harmful impact on the society, in the rare event that it goes viral. This gave rise to a set of heterogenous fact-checking policies across mainstream platforms. For example, Facebook has a substantial partnership program with Fact-checking partners certified by the non-partisan International Fact-Checking Network. Facebook uses a number of signals and machine learning models to predict misinformation and surface it to fact-checkers.\footnote{See the \href{https://www.facebook.com/journalismproject/programs/third-party-fact-checking/how-it-works}{section Frequently asked questions: `How does Facebook use technology to detect potential misinformation?''}} Twitter seems to have a different approach where they focus on providing context rather than fact-checking\footnote{To the best of our knowledge, Twitter does not have a page which summarizes its fact-checking strategy. The Twitter Safety Team tweeted on June 3, 2020 the following:  ``We heard: 1. Twitter shouldn’t determine the truthfulness of Tweets 2. Twitter should provide context to help people make up their own minds in cases where the substance of a Tweet is disputed. Hence, our focus is on providing context, not fact-checking.'' Tweet ID \href{https://twitter.com/TwitterSafety/status/1267986503721988096}{1267986503721988096}.} and the platform is testing a new system based on the wisdom of the crowds to tackle misinformation (see \href{https://blog.twitter.com/en\_us/topics/product/2021/introducing-birdwatch-a-community-based-approach-to-misinformation}{Twitter Birdwatch}). As for Youtube, this platform utilizes the \href{https://schema.org/ClaimReview}{schema.org ClaimReview} markup, where fact-checking articles created by eligible publishers can appear on information panels (see table \ref{summary} in Appendix \ref{links}).

@@

During the COVID19 global health pandemic platforms have upgraded their guidelines to include a set of rules to tackle the propagation of potentially harmful content (see table \ref{summary} in Appendix \ref{links}). Those policies are enforced via existing actions used by the platforms to tackle other rules' violations, such as: labelling content to provide more context or indicate falsehood, publishing a list of terms or topics that will be flagged, suspending accounts, implementing strike systems, reducing the visibility of content, etc. As each platform is a private company, those {\it new} policies are not coordinated and are implemented in different ways across platforms. Such targeted policies show the willingness of mainstream platforms to enhance the quality of the online conversation, but also sheds light on the lack of specific policies to tackle misinformation in general. In particular, policies regarding misinformation are not part of the set of platform rules or community guidelines (as of July 2021). The 2019 report of the Facebook Data Transparency Advisory Group (DTAG) states that ``{\it DTAG was not tasked with evaluating any of the following: (...) Facebook’s policies with respect to “fake news” or misinformation, as neither of these categories were counted as violations within the first two versions of the Community Standards Enforcement Report.}''. Facebook's strategy to tackle ``False News'' is three fold : Remove, Reduce, Inform. It is explained via a blog post on the facebook Newsroom. Similarly, Twitter communicates about actions related to misinformation via their \href{https://blog.twitter.com/en\_us/authors.TwitterSafety}{Twitter Safety} Blog/account. In a post on Youtube Official Blog, the platform explained its ``Four Rs of Responsibility" and how it raises authoritative content, reduces borderline content and harmful misinformation (see table \ref{summary} in Appendix \ref{links}).

@@

Nevertheless, misinformation specific interventions by mainstream platforms are hard to monitor, study or verify by third parties (e.g. academic community, data journalists, NGOs), as in many cases misleading or false content does not qualify as a violation of a given platform's rules and it does not explicitly appear as a separate category in available transparency reports. This makes the study of online misinformation, the assessment of the impact of platforms' actions to tackle misinformation and their relevancy a burdensome task for the academic community. Hence, in the present article we explain how to verify with data mining mainstream platforms' current actions regarding content with low credibility or false information. We do so by providing a series of examples for different interventions and platforms. We only focus on three platforms: Facebook, Twitter and Youtube. Both Facebook and Youtube are in the top three most popular social media platforms in terms of number of users.\footnote{See for example the ranking of the most popular social networks as of April 2021 on Statista: \href{https://www.statista.com/statistics/272014/global-social-networks-ranked-by-number-of-users/}{https://www.statista.com/statistics/272014/global-social-networks-ranked-by-number-of-users/}.} We further choose Twitter because it is a social networking platform with the most news-focused users, according to the Pew Research center (2019)~\cite{pew1}. More specifically, we survey a number of common policies used in order to tackle misinformation, across the three above cited mainstream platforms, Facebook, Twitter and Youtube: temporary or permanent suspension of users, reducing the visibility of some content, introducing flags and notices. We do not provide  an exhaustive list of methods on how to investigate the platforms’ policies. We rather provide a methodology to investigate key policies, that can be useful to researchers or journalists interested in implementing external monitoring. For a detailed list of interventions of multiple platforms we invite the reader to check the following \href{https://airtable.com/shrO0ooI9WSEfIUhb/tblAWQwFOiihKdQjm/viwZLAOzLK1NQ0c2n?blocks=hide}{airtable} compiled by Slatz and Leibowicz (2021)~\cite{niemanlab}.

 We summarize in table \ref{tab1} the tools used to collect the data from Facebook, Twitter and Youtube, that we use in multiple examples throughout the present article. We compile in Appendix \ref{links} in table \ref{summary}, a list of links that redirect to the policies, regulations and transparency centers of Facebook, Twitter and Youtube that we discuss throughout the article. Finally, we discuss how an increased effort of transparency regarding specific content can help the community of researchers study and assess the impact of platforms' policies regarding misinformation.  %the announced policy for a specific user was implemented or not.

@@

Mainstream social media platforms may suspend the account of a specific user when they deem that the platforms' rules have been violated. Account suspension can be temporary or permanent.  When the suspension is temporary the user is prohibited for a limited period of time from posting content on their account, but created content prior to suspension remains available to the user and their followers. However, when the suspension is permanent, in most cases, followers or subscribers have no longer access to the content prior to the suspension and the user can no longer use the account to create new content.  In what follows, we focus on the implementation of this policy by several platforms and provide simple examples to illustrate.

@@

Facebook can also apply a temporary suspension, and in this case the data can often be collected and analyzed. For example, \href{https://www.facebook.com/DonaldTrump/}{Donald Trump’s official Facebook page}  has been suspended following the Capitol attack on January 6, 2021.\footnote{See \href{https://www.facebook.com/zuck/posts/10112681480907401}{https://www.facebook.com/zuck/posts/10112681480907401}} Nevertheless the page’s data is still present in the CrowdTangle API. Thus, after manually adding this page to the CrowdTangle dashboard, we collected the $6$ $083$ posts it had published between January $1$, $2020$ and June $15$, $2021$ using the {\it posts} endpoint.\footnote{See the endpoint documentation for more details: \href{https://github.com/CrowdTangle/API/wiki/Posts}{https://github.com/CrowdTangle/API/wiki/Posts}.} We used Minet command line tool \cite{minet} to collect the data. We can verify on figure \ref{fig1_fb} that the {\it Donald J. Trump} page has not published any content since January $6$, 2021, and that this behavior is not consistent with the page’s previous activity: an average of $16$ posts were published each day on Facebook before the suspension.

@@

%paragraph strike system + say following example is a manual decision. 
Twitter has implemented a strike system as part of their Civic Integrity Policy and their COVID-19 misleading information policy. Violations of both policies can entail strikes, where two strikes lead to a 12-hour account lock and five or more strikes lead to permanent suspension from the platform. A list of notable Twitter temporary and permanent suspensions can be found on  \href{https://en.wikipedia.org/wiki/Twitter_suspensions}{Wikipedia}. The 12-hour account lock is hard to observe in the data, especially for users who do not have an over the clock tweeting activity. In this section, we provide one example of a temporary suspension of a Twitter account, that seems to be the result of a manual decision concerning a Tweet which violated the rules.

The Twitter account $@LifeSite$ of the website lifesitenews.com has been suspended for at least two periods of time: from end of 2019 until fall 2020 for 308 days, then again since January 2021 for having violated Twitter Rules\footnote{See Lifesitenews's article discussing the reason for the suspension: \href{https://www.lifesitenews.com/news/lifesite-is-dumping-twitter-and-so-should-you}{https://www.lifesitenews.com/news/lifesite-is-dumping-twitter-and-so-should-you}. Twitter rules can be found at: \href{https://help.twitter.com/en/rules-and-policies/twitter-rules}{https://help.twitter.com/en/rules-and-policies/twitter-rules}. }. In particular, this website has several failed fact-checks concerning the published articles, according to Iffy.news.\footnote{See \href{https://mediabiasfactcheck.com/life-site-news/}{https://mediabiasfactcheck.com/life-site-news/}}. We collected the activity (tweets, replies, quotes, retweets) on their Twitter account via the Twitter API, using the historical search endpoint. We then plotted the number of Tweets, Retweets, Quotes and Replies per day, as shown in panel $a$ of figure \ref{fig2}). The two periods of temporary suspension are clearly observed in the data as the user(s) of the account were not allowed to use the functionalities of the Twitter Platform.

@@

In this section, we turn to the channel's temporary or permanent suspension policy of Youtube. Whenever a channel publishes a video that violates the community guidelines for the first time they will  usually receive a warning and the content will be removed. For the second time the channel will start receiving strikes. A first strike results in limiting the access of the Youtube channel  for one week, like uploading videos, streaming and other activities. Then a second strike is similar but the suspension will be for two weeks. A third strike results in the termination of the channel. The strike count of a channel lasts 90 days.  In the special case, where a video is in extreme violation of the guidelines, the publishing channel may get terminated without a warning. To illustrate the implementation of this policy we provide two examples for the temporary suspension of the following two Youtube channels: \href{https://www.youtube.com/channel/UCNbIDJNNgaRrXOD7VllIMRQ}{One America news Network} and \href{https://www.youtube.com/user/TonyHeller1}{Tony Heller}.

@@

First, we investigate the temporary suspension case of the Youtube Channel of {\it One America News channel}. This channel received a first strike on November 24, 2020 for the promotion of  a false cure for COVID-19.\footnote{See nbcnews,  \href{https://www.nbcnews.com/news/all/youtube-suspends-oann-violating-its-covid-19-policy-n1248845}{YouTube suspends OANN for violating its Covid-19 policy} nbcnews, Ahiza García-Hodges, 24 11 2020.} We collected the activity of the channel OANN (video counts, view counts) using  the Youtube API v3, between November 2020 and January 2021. For the video counts, we used the playlist endpoint to retrieve the videos uploaded with their publishing date and for the view count we used the IDs of the videos we had from the playlists and via the videos endpoint we retrieved the view counts on June 2021.%\footnote{See the Google documentation  \href{https://developers.google.com/youtube/v3/docs/videos/list}{https://developers.google.com/youtube/v3/docs/videos/list} and \href{https://developers.google.com/youtube/v3/docs/playlists/list}{https://developers.google.com/youtube/v3/docs/playlists/list}}

@@

We first searched for all the Facebook posts having shared a link rated as ‘False’ by Science Feedback with the {\it search} endpoint in minet\footnote{ Click \href{https://beforeitsnews.com/eu/2021/04/stay-away-from-the-vaxxed-it-is-official-from-pfizers-own-documents-2671454.html}{here} to access the link and  \href{https://healthfeedback.org/claimreview/insufficient-evidence-to-claim-covid-19-vaccines-cause-menstrual-irregularities-in-vaccinated-women-vaccinated-people-arent-making-unvaccinated-people-ill/}{its fact-check by Health Feedback}.}. Twenty Facebook posts were collected this way, and the newly developed scraper was used to verify whether they were flagged with an information banner, a fact-check flag, both or none. Three posts were unavailable, and thus could not be categorized by the scraper. As Science Feedback has sent a False fact-check for this link to Facebook, we would expect all these posts to contain a fact-check flag, but we had no expectations for the information banner.

@@

Alongside other social networking platforms, when the content of a tweet violates the Twitter rules, a notice can be added to provide more context according to Twitter's Help Center. At the tweet level, notices take the form of a label or an interstitial. Labels are context specific (e.g. COVID-19 or presidential elections) and  redirect users to a webpage to get more context, for example {\it Get the facts about COVID-19'} (see right panel of figure \ref{fig8}). Interstitials are presented as a greyed box on top of a tweet, which indicate sensitive content, violations of Twitter rules, withheld tweets for violation of local laws or even tweets from suspended accounts, for example {\it The following media includes potentially sensitive content} (see left panel of figure \ref{fig_notice}). At the account level, notices can also indicate whether an account has been temporarily or permanently suspended.

@@

\begin{figure}[h]
\centering
	%\begin{multicols}{1}
		\includegraphics[scale=0.35]{./img/tweets/Capture_2021-06-30_2.png}
   	 %\end{multicols}
	%\begin{multicols}{1} 
		\includegraphics[scale=0.32]{./img/tweets/Capture_2021-06-30.png}
	%\end{multicols}
	\caption{Two tweets sharing the same link marked as False by Science Feedback, screenshots taken on June $20$, 2021. Panel (a): Tweet ID \href{https://twitter.com/davidjcaron/status/1241088065462026242}{1241088065462026242} without a label. Panel (b): Tweet ID \href{https://twitter.com/reactiveIntent/status/1261876171584745472}{1261876171584745472} containing a label.}
	\label{fig8}
\end{figure}

@@

In this section, we take a deeper look at how labels and notices are introduced by Twitter, to indicate content which is inaccurate or false. To that end, we gathered a set of $3094$ links redirecting to articles which were marked as $False$ between April $2019$ and February $2021$ by Science Feedback, a fact-checking organization verifying the credibility of science-related viral information. As a second step, we collected (on June $30$, $2021$) via Minet Command line tool~\cite{minet} all the tweets that have shared a link which belongs to the set of $3094$ links marked as $False$. This data collection resulted in $323$ $938$ tweets, excluding retweets. Only $28$ tweets contained the label { \it Get the facts about COVID-19}, $5$ tweets contained the label {\it Learn about US 2020 election security efforts} and only $1$ had the following label {\it This claim about election fraud is disputed}. Furthermore, we noticed that the labeling rule might not be applied uniformly on a given set of tweets sharing the exact same link, among the set of collected tweets. To give an example, $657$ tweets had shared the exact same link redirecting to a video on Bitchute, entitled {\it Important information on coronavirus 5G Kung Flu}. Among those $657$ tweets only $3$ contained the label {\it Get the facts about COVID-19} (see figure \ref{fig8}). This points towards the non-automation of the tweet labelling process and that it might be that these $3$ tweets were the only ones reported by other users.

@@

We further examine the placement of interstitials that indicate a possibly sensitive content. We find that only $9344$ ($2.97\%$) tweets out of $323$ $938$ containing a link marked as False, have an interstitial {\it potentially sensitive content}. To check whether the interstitial {\it potentially sensitive content} is automated or not, we pick out one tweet having shared a link marked as False\footnote{The link marked as False redirects to the article {\it 5G Technology and induction of coronavirus in skin cells – US National Library of Medicine (what David Icke has been saying for months) } and can be found \href{https://davidicke.com/2020/07/22/5g-technology-and-induction-of-coronavirus-in-skin-cells-us-national-library-of-medicine-what-david-icke-has-been-saying-for-months/}{here}.}, which also contains the interstitial {\it potentially sensitive content}. Then we look in the set of $323$ $938$ tweets for other tweets who have shared the exact same link. We find a total of $32$ tweets. Among those $32$ tweets only $5$ tweets had the interstitial ``potentially sensitive content''. Again this points towards the non-automation of interstitials placement. Furthermore, notice that the appearance of interstitials may depend on the settings of a user's account and country or language specific regulations. In particular, in the settings of Twitter account, one can deactivate the display of interstitials for {\it sensitive content}, by ticking the box {\it Display media that may contain sensitive content} in the section {\it content you see}.

Finally, the number of tweets containing the interstitial {\it potentially sensitive content} ($9344$ tweets) widely outnumbers the tweets which contain a flag ($32$ tweets), among the set of $323$ $938$ tweets containing a link marked as False (see table \ref{flags_tab}). Furthermore, we noticed that among the tweets which contain the interstitial {\it potentially sensitive content}, there are tweets which contain links redirecting to misleading articles about COVID-19 and yet they are not marked by the flag { \it Get the facts about COVID-19}. We also noticed that the $9344$ tweets marked with the interstitial {\it potentially sensitive content} do not necessarily contain graphic violent\footnote{The Twitter Help center explains the placement of interstitials of possibly sensitive content as follows: ``We may place some forms of sensitive media like adult content or graphic violence behind an interstitial advising viewers to be aware that they will see sensitive media if they click through''.} content but rather links that redirect to articles marked as $False$ by Science Feedback. When navigating through the Twitter Help Center, we found no explanation for this large discrepancy between using the interstitial {\it potentially sensitive content} and flags which provide more context to users.\footnote{Twitter Safety account announced in a Tweet (see Tweet ID : \href{https://twitter.com/TwitterSafety/status/1379515615954620418}{1379515615954620418}) on April 6, 2021 that their team ``will begin deploying automated tools to build on (their) efforts to label tweets that may contain misleading information around COVID-19 vaccinations".}
